### 2008-09-22 trunk/Papers/rmrs-08/conclusion.tex
version for Ann

In this paper, we have motivated and defined \rmrs---a semantic
framework that has been used to represent, compare, and combine
semantic information computed from deep and shallow parsers.  \rmrs\
is designed to be maximally flexible on the type of semantic
information that can be left underspecified -- it can underspecify
lexical ambiguity, predicate-argument relations, and scope --, so that
the semantic output of a shallow parser needn't over-determine or
under-determine the semantic information that can be extracted from
the shallow syntactic analysis.  This lays the formal foundations for
a semantic representation formalism that is emerging as a standard in
robust semantic processing.

We then defined the concept of \emph{solved forms} of an \rmrs, in
analogy to dominance graphs.  Solved forms abstract away from
irrelevant differences between models, and have been a crucial concept
in the development of efficient solvers for dominance graphs.  In the
future, we hope to draw upon that body of literature to develop
efficient algorithms for processing \rmrs s, including solvers which
will compute fully specific semantic representations from an \rmrs,
efficient inference algorithms, and algorithms for entailment
checking.  We have argued that entailment is a central notion in
comparing the outputs of different NLP tools, and provided a syntactic
characterization for \rmrs\ entailment, which we hope will allow us to
develop efficient entailment algorithms in the future.

>>>>

In this paper, we have motivated and defined \rmrs---a semantic
framework that has been used to represent, compare, and combine
semantic information computed from deep and shallow parsers.  \rmrs\
is designed to be maximally flexible on the type of semantic
information that can be left underspecified, so that
the semantic output of a shallow parser needn't over-determine or
under-determine the semantic information that can be extracted from
the shallow syntactic analysis.  This lays the formal foundations for
a semantic representation formalism that is emerging as a standard in
robust semantic processing.

We then defined the concept of \emph{solved forms} of an \rmrs, in
analogy to dominance graphs.  Solved forms abstract away from
irrelevant differences between models, and have been a crucial concept
in the development of efficient solvers for dominance graphs.  In the
future, we hope to draw upon that body of literature to develop
efficient algorithms for processing \rmrs s, including solvers which
will compute fully specific semantic representations from an \rmrs,
efficient inference algorithms, and algorithms for entailment
checking.  We have argued that entailment is a central notion in
comparing the outputs of different {\sc nlp} tools, and provided a syntactic
characterization for \rmrs\ entailment, which we hope will allow us to
develop efficient entailment algorithms in the future.

### 2008-09-22 trunk/Papers/rmrs-08/entailment.tex
version for Ann

\begin{thm}\label{thm:big-one}
  Let $\varphi, \varphi'$ be two {\sc rmrs}s.  Then $\varphi \models
  \varphi'$ iff for every solved form $S$ of $\varphi$, there is a
  solved form $S'$ of $\varphi'$ such that $S$ is an extension of
  $S'$. \todo{We don't know if this is true for qeq; the proof is
    written for $\dom$.}  \todo{Also note that this is about a version
    of entailment in which $\varphi$ and $\varphi'$ contain the same
    variables, which makes the claim a bit weaker.}
\end{thm}
\begin{proof}[Proof (sketch)]
``$\Leftarrow$'' follows from
Props.~\ref{prop:solved-forms-are-satisfiable} and
\ref{prop:models-satisfy-solved-forms}.

``$\Rightarrow$'': The basic idea is to construct a solved form for
$\varphi'$ by choosing a solved form for $\varphi$ and removing all
atoms using variables that don't occur in $\varphi'$.  The hard part
is the proof that the result is a solved form of $\varphi'$; this step
involves proving that if $\varphi \models \varphi'$, then all EPs in
$\varphi'$ also occur in $\varphi$.  
\end{proof}

>>>>

\begin{thm}\label{thm:big-one}
  Let $\varphi, \varphi'$ be two {\sc rmrs}s.  Then $\varphi \models
  \varphi'$ iff for every solved form $S$ of $\varphi$, there is a
  solved form $S'$ of $\varphi'$ such that $S$ is an extension of
  $S'$. \todo{Check proof holds for this version.}
% Do we have a proof where $\varphi$ and $\varphi'$ can vary on
% alphabetic variance on nodes and base variables?
\end{thm}
\begin{proof}[Proof (sketch)]
``$\Leftarrow$'' follows from
Props.~\ref{prop:solved-forms-are-satisfiable} and
\ref{prop:models-satisfy-solved-forms}.

``$\Rightarrow$'': The basic idea is to construct a solved form for
$\varphi'$ by choosing a solved form for $\varphi$ and removing all
atoms using variables that don't occur in $\varphi'$.  The hard part
is the proof that the result is a solved form of $\varphi'$; this step
involves proving that if $\varphi \models \varphi'$, then all {\sc ep}s in
$\varphi'$ also occur in $\varphi$.  
\end{proof}

### 2008-09-22 trunk/Papers/rmrs-08/introduction.tex
version for Ann

There are certain semantic phenomena that these robust
approaches don't capture reliably, including quantifier scope,
optional arguments, and long-distance dependencies (for instance,
\newcite{clark:etal:2004} report that the parser used by
\newcite{bos:etal:2004} yields only 63\% accuracy on object
extraction; e.g., {\em the man that I met\dots}).  Forcing a shallow
parser to make a decision about these phenomena can therefore be
error-prone.  Depending on the application, it may be preferrable to
give the parser the option to leave the decision open when it's not
sufficiently informed---i.e., to compute a partial semantic
representation and to complete it later, using information
extraneous to the parser.

In this paper, we focus on one particular approach to representing
partial semantic information: Robust Minimal Recursion Semantics
(\rmrs, \cite{copestake:2003}).  \rmrs\ is a generalisation of \mrs\
\cite{copestake:etal:2005} that is designed to support
underspecification of scope and predicate-argument structure.  It is
an emerging standard representation language for partial semantic
information, and has been applied in several implemented systems.  For
instance, \newcite{copestake:2003} and \newcite{frank:2004} use it to
specify semantic components to shallow parsers ranging in depth from
{\sc pos} taggers to chunk parsers and intermediate parsers such as
{\sc rasp} \cite{briscoe:etal:2006}.  {\sc mrs} analyses derived from
deep grammars, such as the English Resource Grammar ({\sc erg},
\cite{copestake:flickinger:2000}) are special cases of {\sc
  rmrs}.

However, from a formal perspective, \rmrs\ is somewhat ad-hoc in that
it has no clearly defined model theory; i.e., what exactly, any given
\rmrs\ representation actually \emph{means} is not defined.  The key
contribution we make is to cast {\sc rmrs}, for the first time, as a
logic with a well-defined model theory.  This has a number of
advantages.  First, it allows us to formally relate \rmrs\ to other
frameworks such as \mrs\ and predicate logic in order to establish the
compatibility of \rmrs\ with the approaches to robust semantic
analysis mentioned above.  
Second, it provides us with a notion of logical
entailment, which we can use to verify the compatibility of \rmrs\ 
representations computed from different parsers, such as a deep and a
shallow parser.  Finally, it is only through rigid formalisation that
we can give users of \rmrs\ access to inference systems and to
algorithms for efficiently computing the possible fully specific
semantic representations described by the \rmrs\ output of a shallow
parser.

Section~\ref{sec:motivation} illustrates via example the differences
and challenges with deep and shallow semantic construction.
Section~\ref{sec:rmrs} defines the syntax and model-theory of \rmrs\.
In Section~\ref{sec:entailment} we demonstrate the practical
usefulness of our formalisation by modelling compatibility of partial
semantic representations as \rmrs\ entailment and by providing a
syntactic criterion for characterising entailment.
Section~\ref{sec:conclusion} concludes and points to future work.

>>>>

There are certain semantic phenomena that these robust
approaches don't capture reliably, including quantifier scope,
optional arguments, and long-distance dependencies (for instance,
\newcite{clark:etal:2004} report that the parser used by
\newcite{bos:etal:2004} yields only 63\% accuracy on object
extraction; e.g., {\em the man that I met\dots}).  Forcing a shallow
parser to make a decision about these phenomena can therefore be
error-prone.  Depending on the application, it may be preferrable to
give the parser the option to leave a semantic decision open when it's not
sufficiently informed---i.e., to compute a partial semantic
representation and to complete it later, using information
extraneous to the parser.

In this paper, we focus on an approach to representing partial
semantic information that supports this strategy: Robust Minimal
Recursion Semantics (\rmrs, \cite{copestake:2003}).  \rmrs\ is a
generalisation of \mrs\ \cite{copestake:etal:2005} that is designed to
support underspecification of scope and predicate-argument structure.
It is an emerging standard for representing partial
semantic information, and has been applied in several implemented
systems.  For instance, \newcite{copestake:2003} and
\newcite{frank:2004} use it to specify semantic components to shallow
parsers ranging in depth from {\sc pos} taggers to chunk parsers and
intermediate parsers such as {\sc rasp} \cite{briscoe:etal:2006}.
{\sc mrs} analyses derived from deep grammars, such as the English
Resource Grammar ({\sc erg}, \cite{copestake:flickinger:2000}) are
special cases of {\sc rmrs}.

However, from a formal perspective, \rmrs\ is somewhat ad-hoc in that
it has no clearly defined model theory; i.e., what exactly any given
\rmrs\ representation actually \emph{means} is not defined.  The key
contribution we make is to cast {\sc rmrs}, for the first time, as a
logic with a well-defined model theory.  This has a number of
advantages.  First, it allows us to formally relate \rmrs\ to other
frameworks such as \mrs\ and predicate logic in order to establish the
compatibility of \rmrs\ with the approaches to robust semantic
analysis mentioned above.  
Second, it provides us with a notion of logical
entailment, which we can use to verify the compatibility of \rmrs\ 
representations computed from different parsers, such as a deep and a
shallow parser.  Finally, it is only through rigid formalisation that
we can give users of \rmrs\ access to inference systems and to
algorithms for efficiently computing the possible fully specific
semantic representations described by the \rmrs\ output of a shallow
parser.

Section~\ref{sec:motivation} illustrates via example the differences
and challenges with deep and shallow semantic construction.
Section~\ref{sec:rmrs} defines the syntax and model-theory of \rmrs.
In Section~\ref{sec:entailment} we demonstrate the practical
usefulness of our formalisation by modelling compatibility of partial
semantic representations as \rmrs\ entailment and by providing a
syntactic criterion for characterising entailment.
Section~\ref{sec:conclusion} concludes and points to future work.

### 2008-09-22 trunk/Papers/rmrs-08/motivation.tex
version for Ann

This sentence exhibits several kinds of ambiguity, including a scope
ambiguity between ``every fat cat'' and ``some dog'' and lexical
ambiguities of the words ``cat'' and ``dog'' (which have 8 and 7 noun
senses according to Wordnet, respectively).  Two of these readings are
shown as logical forms below; they can be represented as trees as
shown in Fig.~\ref{fig:1}.

\begin{examples}
\item $\sem{\_every\_q\_1}(x, \sem{\_fat\_j\_1}(e',x) \wedge
    \sem{\_cat\_n\_1}(x),$\\
\hspace*{0.1in} $\sem{\_some\_q\_1}(y, \sem{\_dog\_n\_1}(y),$\\
\hspace*{0.2in}$\sem{\_chased\_v\_1}(e,x,y)))$
\label{ex:fat-cat-1}
\item $\sem{\_some\_q\_1}(y, \sem{\_dog\_n\_2}(y),$\\
\hspace*{0.1in}$\sem{\_every\_q\_1}(x, \sem{\_fat\_j\_1}(e',x) \wedge
    \sem{\_cat\_n\_2}(x), $\\
\hspace*{0.2in}$\sem{\_chased\_v\_1}(e,x,y)))$
\label{ex:fat-cat-2}
\end{examples}

@@

Now imagine that we are trying to extract semantic information from
the output of a part-of-speech tagger by using the word lemmas as
lexical predicate symbols.  Such a semantic representation is highly
partial, as it will not say anything about predicate-argument
relations or resolve lexical ambiguity -- it will use predicate
symbols such as $\sempred{\_cat\_n}$, which might resolve to the
predicate symbols $\sem{\_cat\_n\_1}$ or $\sem{\_cat\_n\_2}$ in the
complete semantic representation.  (Notice that we are using different
fonts for the ambiguous and unambiguous predicate symbols.)  
We can
express this information in \rmrs\ as follows.

\begin{examples}
\item \label{ex:cat-pos}
$l_1:a_1:\sempred{\_every\_q}(x_1)$, \\
$l_{41}:a_{41}:\sempred{\_fat\_a}(e')$,\\
$l_{42}:a_{42}:\sempred{\_cat\_n}(x_3)$\\
$l_5:a_5:\sempred{\_chased\_v}(e_{past})$, \\
$l_6:a_6:\sempred{\_some\_q}(x_6)$, \\
$l_9:a_9:\sempred{\_dog\_n}(x_7)$
\end{examples}

@@

There are of course many other trees (and thus, fully specific
semantic representations such as (\ref{ex:fat-cat-1})) that are
described equally well by the same \rmrs; this is not surprising,
given that the semantic information we got from the POS tagger is so
incomplete.  If we have more information, say information about
subject and object relations from a chunk parser like Cass
\cite{abney:1996}, we can represent these in a more
detailed \rmrs, as follows:

\begin{examples}
\item 
$l_1:a_1:\sempred{\_every\_q}(x_1)$, \\
$l_{41}:a_{41}:\sempred{\_fat\_a}(e')$,\\
$l_{42}:a_{42}:\sempred{\_cat\_n}(x_3)$\\
$l_5:a_5:\sempred{\_chased\_v}(e_{past})$, 
\hspace*{0.1in} $\ARG1(a_5,x_4),
\ARG2(a_5,x_5)$\\ 
$l_6:a_6:\sempred{\_some\_q}(x_6)$, \\
$l_9:a_9:\sempred{\_dog\_n}(x_7)$\\
$x_3=x_4$, $x_5=x_7$
\label{ex:cat-partial-parser}
\end{examples}

This \rmrs\ uses two new types of atoms.  Atoms of the form $x_3=x_4$
express that the two variables $x_3$ and $x_4$ must map to the same
variable in any fully specific logical form; e.g., to the variable $x$
in Fig.~\ref{fig:1}.  Atoms of the form
$\ARG_i(a,x)$ and $\ARG_i(a,h)$ express that the $i$-th child of the
node to which the anchor $a$ refers is the variable name that $x$ maps
to (or the node that the {\em hole} $h$ denotes).  The separation of
{\sc ep}s and $\ARG$ atoms is perhaps the most important difference between
\rmrs\ and earlier underspecification formalisms such as \mrs\ and
dominance graphs, which required that a predicate and its arguments
had to be specified together.  \rmrs\ goes beyond these formalisms in
expressive power, because it allows one to state separately
information about how many arguments a predicate takes, and the values of
those (non-scopal and scopal) arguments.   If we also allow atoms of the form
$\ARG_{\{2,3\}}(a,x)$ to express uncertainty as to whether $x$ is the
second or third child of the anchor $a$, then \rmrs\ can specify the
arguments to a predicate while underspecifying their position.

Finally, here is an \rmrs\ that could be derived from a deep grammar
such as the ERG:

\begin{examples}
\item $l_1:a_1\handel\mbox{\_every\_q\_1}(x_1),$\\
\hspace*{0.1in}$\mbox{RSTR}(a_1,h_2),
\mbox{BODY}(a_1,h_3)$\\ 
$l_{41}:a_{41}\handel\mbox{\_fat\_j\_1}(e'), \ARG1(a_{41},x_2)$\\
$l_{42}:a_{42}\handel\mbox{\_cat\_n\_1}(x_3)$\\
$l_5:a_5\handel\mbox{\_chase\_v\_1}(e_{spast})$,\\
\hspace*{0.1in}$\ARG1(a_5,x_4),
\ARG2(a_5,x_5)$\\ 
$l_6:a_6\handel\mbox{\_some\_q\_1}(x_6)$,\\
\hspace*{0.1in}$\mbox{RSTR}(a_6,h_7),
\mbox{BODY}(a_6,h_8)$\\ 
$l_9:a_9\handel\mbox{\_dog\_n\_1}(x_7)$\\
$h_2=_q l_{42}, l_{41}=l_{42}, h_7 =_q l_9$\\
$x_1=x_2, x_2=x_3, x_3=x_4,$\\
$x_5=x_6, x_5=x_7$
\label{ex:cat-erg}
\end{examples}
RSTR and BODY are conventional names for the scopal arguments to
predicate symbols corresponding to quantifiers.  
This is now an extremely detailed underspecified representation of the
different semantic representations of the sentence, which is
essentially a notational variant of the \mrs\ that the {\sc erg} would
derive.  Notice the use of atoms like $h_2 \qeq l_{42}$, which specify
a kind of ``outscopes'' relationship between the hole and the label,
and can be used to underspecify the scope of the two quantifiers.

Notice also that the labels of the EPs for ``fat'' and ``cat'' are
stipulated to be equal in the \rmrs\ (\ref{ex:cat-erg}), whereas the
anchors are not. 
In the tree, it is the anchors that are mapped to the nodes with the
labels $\sem{\_fat\_a\_1}$ and $\sem{\_cat\_n\_1}$; the label is
mapped to the conjunction node just above them.  In other words, the
role of the anchor in an {\sc ep} is to connect a predicate to its
arguments, while the role of the label is to connect the {\sc ep} to the
surrounding formula.  Representing conjunction with label sharing
stems from \mrs\ and provides compact semantic representations.

In summary, \rmrs\ is a formalism for representing partial information
about semantic representations.  It generalizes \mrs\ in that it can
represent the output of a deep grammar in a way that is a notational
variant of \mrs; but in cases in which a deep grammar is not
available, it can be used to capture whatever partial semantic
information a shallower NLP tool was able to provide.  \rmrs\ is
designed to serve as a generic formalism for partial semantic
representations which abstracts over the details of different NLP
tools and allows us to represent, process, and compare information
from different tools in the same formalism, and in the long run
provide a platform for incrementally enriching partial information
such as (\ref{ex:cat-pos}) in order to eventually approximate more
detailed representations such as (\ref{ex:cat-partial-parser}).

>>>>

This sentence exhibits several kinds of ambiguity, including a scope
ambiguity between ``every fat cat'' and ``some dog'' and lexical
ambiguities of the words ``cat'' and ``dog'' (which have 8 and 7 noun
senses according to Wordnet, respectively).  Simplifying slightly by
ignoring tense information (but see
Section~\ref{sec:extensions}), two of these readings are
shown as logical forms below; they can be represented as trees as
shown in Fig.~\ref{fig:1}.

\begin{examples}
\item $\sem{\_every\_q\_1}(x, \sem{\_fat\_j\_1}(e',x) \wedge
    \sem{\_cat\_n\_1}(x),$\\
\hspace*{0.1in} $\sem{\_some\_q\_1}(y, \sem{\_dog\_n\_1}(y),$\\
\hspace*{0.2in}$\sem{\_chase\_v\_1}(e,x,y)))$
\label{ex:fat-cat-1}
\item $\sem{\_some\_q\_1}(y, \sem{\_dog\_n\_2}(y),$\\
\hspace*{0.1in}$\sem{\_every\_q\_1}(x, \sem{\_fat\_j\_1}(e',x) \wedge
    \sem{\_cat\_n\_2}(x), $\\
\hspace*{0.2in}$\sem{\_chase\_v\_1}(e,x,y)))$
\label{ex:fat-cat-2}
\end{examples}

@@

Now imagine that we are trying to extract semantic information from
the output of a part-of-speech tagger by using the word lemmas as
lexical predicate symbols.  Such a semantic representation is highly
partial, as it will not say anything about predicate-argument
relations or resolve lexical ambiguity---it will use predicate
symbols such as $\sempred{\_cat\_n}$, which might resolve to the
predicate symbols $\sem{\_cat\_n\_1}$ or $\sem{\_cat\_n\_2}$ in the
complete semantic representation.  (Notice that we are using different
fonts for the ambiguous and unambiguous predicate symbols.)  
We can
express this information in \rmrs\ as follows.

\begin{examples}
\item \label{ex:cat-pos}
$l_1:a_1:\sempred{\_every\_q}(x_1)$, \\
$l_{41}:a_{41}:\sempred{\_fat\_a}(e')$,\\
$l_{42}:a_{42}:\sempred{\_cat\_n}(x_3)$\\
$l_5:a_5:\sempred{\_chase\_v}(e)$, \\
$l_6:a_6:\sempred{\_some\_q}(x_6)$, \\
$l_9:a_9:\sempred{\_dog\_n}(x_7)$
\end{examples}

@@

There are of course many other trees (and thus, fully specific
semantic representations such as (\ref{ex:fat-cat-1})) that are
described equally well by the \rmrs\ (\ref{ex:cat-pos}); this is
not surprising, 
given that the semantic information we got from the {\sc pos} tagger is so
incomplete.  If we have more information, say information about
subject and object relations from a chunk parser like Cass
\cite{abney:1996}, we can represent these in a more
detailed \rmrs, as follows:

\begin{examples}
\item 
$l_1:a_1:\sempred{\_every\_q}(x_1)$, \\
$l_{41}:a_{41}:\sempred{\_fat\_a}(e')$,\\
$l_{42}:a_{42}:\sempred{\_cat\_n}(x_3)$\\
$l_5:a_5:\sempred{\_chase\_v}(e)$, \\
\hspace*{0.1in} $\ARG1(a_5,x_4),
\ARG2(a_5,x_5)$\\ 
$l_6:a_6:\sempred{\_some\_q}(x_6)$, \\
$l_9:a_9:\sempred{\_dog\_n}(x_7)$\\
$x_3=x_4$, $x_5=x_7$
\label{ex:cat-partial-parser}
\end{examples}

This \rmrs\ uses two new types of atoms.  Atoms of the form $x_3=x_4$
express that the two variables $x_3$ and $x_4$ must map to the same
variable in any fully specific logical form; e.g., to the variable $x$
in Fig.~\ref{fig:1}.  Atoms of the form
$\ARG_i(a,z)$ and $\ARG_i(a,h)$ express that the $i$-th child
(counting from 0) of the
node to which the anchor $a$ refers is the variable name that $z$ denotes
(or the node that the {\em hole} $h$ denotes).  The separation of
{\sc ep}s and $\ARG$ atoms is perhaps the most important difference between
\rmrs\ and earlier underspecification formalisms such as \mrs\ and
dominance graphs, which required that a predicate and its arguments
had to be specified together.  \rmrs\ goes beyond these formalisms in
expressive power, because it allows one to state separately
information about how many arguments a predicate takes (which is
necessary for supporting parsers where information about lexical
subcategorisation is absent), and the values of
those (non-scopal and scopal) arguments.   If we also allow atoms of the form
$\ARG_{\{2,3\}}(a,x)$ to express uncertainty as to whether $x$ is the
second or third child of the anchor $a$, then \rmrs\ can specify the
arguments to a predicate while underspecifying their position.

Finally, \rmrs\ (\ref{ex:cat-erg}) is a notational variant of the {\sc
  mrs} derived by the {\sc erg}, a wide-coverage deep grammar:
\begin{examples}
\item $l_1:a_1\handel\mbox{\_every\_q\_1}(x_1),$\\
\hspace*{0.1in}$\mbox{RSTR}(a_1,h_2),
\mbox{BODY}(a_1,h_3)$\\ 
$l_{41}:a_{41}\handel\mbox{\_fat\_j\_1}(e'), \ARG1(a_{41},x_2)$\\
$l_{42}:a_{42}\handel\mbox{\_cat\_n\_1}(x_3)$\\
$l_5:a_5\handel\mbox{\_chase\_v\_1}(e)$,\\
\hspace*{0.1in}$\ARG1(a_5,x_4),
\ARG2(a_5,x_5)$\\ 
$l_6:a_6\handel\mbox{\_some\_q\_1}(x_6)$,\\
\hspace*{0.1in}$\mbox{RSTR}(a_6,h_7),
\mbox{BODY}(a_6,h_8)$\\ 
$l_9:a_9\handel\mbox{\_dog\_n\_1}(x_7)$\\
$h_2=_q l_{42}, l_{41}=l_{42}, h_7 =_q l_9$\\
$x_1=x_2, x_2=x_3, x_3=x_4,$\\
$x_5=x_6, x_5=x_7$
\label{ex:cat-erg}
\end{examples}
RSTR and BODY are conventional names for the scopal arguments to
predicate symbols corresponding to quantifiers.   
Atoms like $h_2 \qeq l_{42}$ specify
a kind of ``outscopes'' relationship between the hole and the label,
and can be used to underspecify the scope of the two quantifiers.
Notice also that the labels of the {\sc ep}s for ``fat'' and ``cat'' are
stipulated to be equal in the \rmrs\ (\ref{ex:cat-erg}), whereas the
anchors are not. 
In the tree, it is the anchors that are mapped to the nodes with the
labels $\sem{\_fat\_a\_1}$ and $\sem{\_cat\_n\_1}$; the label is
mapped to the conjunction node just above them.  In other words, the
role of the anchor in an {\sc ep} is to connect a predicate to its
arguments, while the role of the label is to connect the {\sc ep} to the
surrounding formula.  Representing conjunction with label sharing
stems from \mrs\ and provides compact semantic representations.
Finally, (\ref{ex:cat-erg}) intuitively represents more specific
semantic information than (\ref{ex:cat-partial-parser}), so long as
the base-language constructors that \_cat\_n\_1 can correspond to is a
subset of those that \_cat\_n can correspond to (written
$\mbox{\_cat\_n\_1}\sqsubseteq \mbox{\_cat\_n}$), and similalry for
\_fat\_j\_1 etc.  This is because with these so-called SPEC relations
on the predicate symbols in place, (\ref{ex:cat-erg}) simply adds
ARGs, qeqs and variable equalities to (\ref{ex:cat-partial-parser}).

In summary, \rmrs\ is a formalism for representing partial information
about semantic representations.  It generalizes \mrs\ in that it can
represent the output of a deep grammar in a way that is a notational
variant of \mrs; but in cases in which a deep grammar is not
available, it can be used to capture whatever partial semantic
information a shallower {\sc nlp} tool was able to provide.  \rmrs\ is
designed to serve as a generic formalism for partial semantic
representations which abstracts over the details of different {\sc nlp}
tools and allows us to represent, process, and compare information
from different tools in the same formalism, and in the long run
provide a platform for incrementally enriching partial information
such as (\ref{ex:cat-pos}) in order to eventually approximate more
detailed representations such as (\ref{ex:cat-partial-parser}) or
(\ref{ex:cat-erg}).
